\large Neural and Symbolic Optimization of Cosmological Particle-Mesh Simulation \vspace{0.3em}

### 2024-03-04 docs/papers/sto/so.tex
FIXUP draft: minor

We fit the trained NNs with symbolic regression for analytic
expressions of the $f(k_i; \vvartheta)$ and $g(k_1, k_2, k_3;
\vvartheta)$ functions.

@@

In \autoref{fig:tfcc}, we show the results of $T$ and $r$ for both
training and test data samples.
To show different box sizes, we normalize the wavenumber by the Nyquist
wavenumber $k_{\rm Nyquist} = \pi / l_p$ of the particle grid, where
$l_p$ is the particle spacing.

comparison of PM, PM with SO NN (PM-SONN), PM with SO SR (PM-SOSR)

@@

% density field with zoom in (with halos painted as circles?)
The effect of force sharpening can also be visually shown by looking
directly at the density field.

@@

\subsection{Benchmarks}
We compare the computational cost of \GADGET, \pmwd\ with NNs, and
\pmwd\ with SR.

We time the computation of force sharpening for one step using NNs and
SR respectively.

>>>>

To make the SO more interpretable and applicable to other simulations,
we fit the trained NNs with symbolic regression for analytic
expressions of the $f(k_i; \vvartheta)$ and $g(k_1, k_2, k_3;
\vvartheta)$ functions.

@@

In \autoref{fig:tfcc}, we show the results of TF and CC for both
training and test data samples.
To show different box sizes, we normalize the wavenumber by the Nyquist
wavenumber $k_{\rm Nyquist} = \pi / l_p$ of the particle grid, where
$l_p$ is the particle spacing.
Compared to original PM, the TF of PM-SONN is improved to be consistent
with \GADGET\ within 10\% up to the particle grid Nyquist wavenumber.

@@

The effect of force sharpening can also be visually shown by looking
directly at the higher resolution of the density field
(\autoref{fig:denslab}) on small scales.
Compared to orginal PM, PM-SONN is more similar to \GADGET\ with sharper
big halos and more small-scale structures.

@@

\subsection{Benchmarks}
We compare the computational cost of \GADGET, original PM, PM-SONN, and
PM-SOSR.

The forward evaluation of the NNs is more computation and memory
expensive compared to the analytic expressions.
We time the computation of SO for one step using NNs and SR
respectively.
